An Authoritative Adventure

### 2020-01-05 article.tex
Added a map style option to prefix numbers with a designated character (or string)

>>>>

\section{Alternate Map Region Styles}
Published modules sometimes use plain numbers for locations, sometimes they
prefix a character to the front of the numbers. The following options can be
used to display in these forms:

\numberedarea{Numbered Dungeon}
Areas in the Numbered Dungeon have sequential numbers. This is done using
the following commands:

\begin{verbatim}
\numberedarea{Numbered Dungeon}
\numberedsubarea{Entry}
\numberedsubarea{Trap}
\numberedsubarea{Fight}
\numberedsubarea{Exit}
\end{verbatim}

\numberedsubarea{Entry}
\numberedsubarea{Trap}
\numberedsubarea{Fight}
\numberedsubarea{Exit}

\prefixedarea{Ace Dungeon}{A}
Areas in the Ace Dungeon are prefixed with `\prefixedareaprefix'.
This is done using the following commands:

\begin{verbatim}
\prefixedarea{Ace Dungeon}{A}
\prefixedsubarea{Entry}
\prefixedsubarea{Exit}
\end{verbatim}

\prefixedsubarea{Entry}
\prefixedsubarea{Exit}

\prefixedarea{The Fantastic Zoo}{Z}
Areas in the Fantastic Zoo are prefixed with `\prefixedareaprefix'.

\prefixedsubarea{Entry}
\prefixedsubarea{Exit}
